---
title: "Team Variance Case Study One"
author(s): "Terry Johnson, Brandon de la Houssaya, Justin Castro, Steven Cocke"
date: "6/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case Study One (1)

## How many breweries are present in each State?
```{r Step_1, echo=TRUE}
#Total Breweries by state
# Read in the breweries data
breweries <- read.csv("breweries.csv", header  = TRUE)
# compile the number by state using the aggregate function in R
breweries.by.State <- aggregate( rep(1,dim(breweries)[1]), by=list(breweries$State), sum)
# Update the column names to something more meaningful
colnames(breweries.by.State) <- c("State","Number")
# Sort by state from largest to smallest number of breweries
sortedBreweriesByState <- breweries.by.State[order(breweries.by.State$Number, decreasing = TRUE),]
# Display the Breweries by States in descending order top 6
head(sortedBreweriesByState,6)
# DIsplay as BarChart for easier viewing of a large data set
barplot(sortedBreweriesByState[,2], beside = TRUE, names.arg = sortedBreweriesByState$State,ylab="# Breweries", main = "Brweries By State", xlab = "State")
```

## Merge beer data with the breweries data.  Print the first 6
## observations and the last 6 observation to check the merged 
## data

```{r step_2, echo=TRUE}
# Merge Data and then head(6), then tail(6)
Beer <- read.csv(file="Beers.csv", header=TRUE, sep=",")
Breweries <-read.csv(file="Breweries.csv", header=TRUE, sep=",")

BeerBreweries <- merge(Beer, Breweries, by.x="Brewery_id", by.y="Brew_ID", all=TRUE)
colnames(BeerBreweries) <- c("Brewery_ID","Beer","Beer_ID","ABV","IBU","Style","Ounces","Brewery","City","State")
# First 6 Merged Beer and Breweries
head(BeerBreweries,6)
# Last 6 Merged Beer and Breweries
tail(BeerBreweries,6)
```

## Report the number of NA's in each column

```{r step_3, echo=TRUE}
sum(is.na(BeerBreweries$Brewery_id))
sum(is.na(BeerBreweries$Name.x))
sum(is.na(BeerBreweries$Beer_ID))
sum(is.na(BeerBreweries$ABV))
sum(is.na(BeerBreweries$IBU))
sum(is.na(BeerBreweries$Style))
sum(is.na(BeerBreweries$Ounces))
sum(is.na(BeerBreweries$Name.y))
sum(is.na(BeerBreweries$City))
sum(is.na(BeerBreweries$State))
```


## Compute the median alcohol content and international 
## bitterness unit for each state.  Plot a bar chart to compare.
```{r step_4, echo=TRUE}
BeerBreweriesDF <-na.omit(BeerBreweries)
ByState <- aggregate(BeerBreweriesDF[,4:5], list(BeerBreweriesDF$State), median)
barplot(ByState[,2], beside = TRUE, names.arg = ByState$Group.1,xlab="ABV", main = "Median ABV by State", ylab = "State")
barplot(ByState[,3], beside = TRUE, names.arg = ByState$Group.1,xlab="IBU", main = "Median IBU by State", ylab = "State")
```


## Which State has the maximum alcoholic (ABV) beer? 
## Which state has the most IBU Beer?
```{r step_5, echo=TRUE}
# Max ABV by state
# Max IBU by state
```

## Summary Statistics for the ABV variable.
```{r step_6, echo=TRUE}
# Summary ABV
```


## Is there an apparent relationship between the 
## bitterness of the beer and it's alcoholic content?  
## Draw a scatter plot
```{r step_7, echo=TRUE}
# Relationship
# Scatter Plot
```


