---
title: "Team Variance Case Study One"
author(s): "Terry Johnson, Brandon DeLa Houssaya, Justin, Steven Cocke"
date: "6/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case Study One (1)

## How many breweries are present in each State?
```{r Step_1, echo=TRUE}
# Total by state the number of breweries
```

## Merge beer data with the breweries data.  Print the first 6 observations
## and the last 6 observation to check the merged data

```{r step_2, echo=TRUE}
# Merge Data and then head(6), then tail(6)
```

## Report the number of NA's in each column

```{r step_3, echo=TRUE}
# Count NA's by column
```


## Compute the median alcohol content and international bitterness unit for 
## each state.  Plot a bar chart to compare.
```{r step_4, echo=TRUE}
# Compute Median Alcohol
# Compute IBU
# Bar Chart by state
```


## Which State has the maximum alcoholic (ABV) beer? 
## Which state has the most IBU Beer?
```{r step_5, echo=TRUE}
# Max ABV by state
# Max IBU by state
```

## Summary Statistics for the ABV variable.
```{r step_6, echo=TRUE}
# Summary ABV
```


## Is there an apparent relationship between the bitterness of the beer 
## and it's alcoholic content?  
## Draw a scatter plot
```{r step_7, echo=TRUE}
# Relationship
# Scatter Plot
```
